Verifying Demonstrations

### 2018-05-25 paper/conclusions.tex
Removes fixed comments

>>>>

Finally, Mallory represents another nation state and has some interest in 
affecting the stability of Grace's regime, for Mallory's own gain, thus 
supporting either Grace or Alice as she see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Grace}
In addition, Mallory could also have simply as her objective to cause a 
denial-of-service attack on the architecture of \PRIVO.

Mallory cannot create keys valid in another nation state.

### 2018-05-25 paper/properties.tex
Removes fixed comments

In our setting, we have two potential adversaries: Alice and Grace.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
\daniel{Changed back to Grace since that's what's in the intro now.}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
count but also additionally to deanonymize some of the participants in order to 
arrest them or forcefully convince them to change their minds.
In the following two subsections, we will define the desired security 
properties.

>>>>

In our setting, we have two potential adversaries: Alice and Grace.
Alice is a participant to the protest and thus she might be also interested in 
manipulating the system to increase the count (\eg she might have an incentive 
to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
count but also additionally to deanonymize some of the participants in order to 
arrest them or forcefully convince them to change their minds.
In the following two subsections, we will define the desired security 
properties.
